Type theory with single substitutions

### 2025-02-22 fscd/p.tex
small_fix

In the future, we would like to investigate whether the calculus can
be minimised even more, e.g.\ to the degree that there is only one
equation between any two terms. This would be interesting for a
possible coherent syntax of type theory avoiding the need for
truncation in the setting of homotopy type theory.

>>>>

In the future, we would like to investigate whether the calculus can
be minimised even more, e.g.\ to the degree that there is at most one
proof for any equation. This would be interesting for a possible
coherent syntax of type theory avoiding the need for truncation in the
setting of homotopy type theory.
